Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2022-10-31 analysis/paper/paper.qmd
make the artefact schematic smaller, and the sig tests table show only 3 digits

here::here("analysis/data/raw_data/site-total-artifacts.csv") %>% 
  read.csv() %>% 
  knitr::kable(.)

@@

here::here("analysis/data/raw_data/Korean-paleolithic-chronology.csv") %>% 
  read.csv() %>% 
  knitr::kable(.)

@@

```{r}
#| label: fig-labelled-schematic
#| fig-height: 1
#| fig-cap: Stemmed point from Yongsandong site. with landmarks showing the attributes considered in this study and corresponding landmarks

knitr::include_graphics(here::here("analysis/figures/hand-made-figures/ISKM-talk-2021-cut.png"))
```

@@

here::here("analysis/data/raw_data/table-of-landmark-abbreviations.csv") %>% 
  read.csv() %>% 
  knitr::kable(.)

@@

```{r}
#| label: tbl-cv-over-time

@@

# apply mslr test to each variable (row with a tibble)
# Krishnamoorthy and Lee’s (2014) modified signed-likelihood ratio test
# this is a table we can show in the text
table_mslr_test_results_for_phase_differences <-
  df_sitename_nested %>%
  mutate(mslr_result = map_df(data, ~mslr_test(nr = 1e4,
                                               .$value,
                                               .$SPstage.Stage))) %>%
  unnest(mslr_result) %>%
  dplyr::select(-data)

@@

knitr::kable(table_mslr_test_results_for_phase_differences)

>>>>

here::here("analysis/data/raw_data/site-total-artifacts.csv") %>% 
  read_csv() %>% 
  knitr::kable(.)

@@

here::here("analysis/data/raw_data/Korean-paleolithic-chronology.csv") %>% 
  read_csv() %>% 
  knitr::kable(.)

@@

```{r}
#| label: fig-labelled-schematic
#| fig-cap: Stemmed point from Yongsandong site. with landmarks showing the attributes considered in this study and corresponding landmarks
#| out-width: "300px"

knitr::include_graphics(here::here("analysis/figures/hand-made-figures/ISKM-talk-2021-cut.png"))

@@

here::here("analysis/data/raw_data/table-of-landmark-abbreviations.csv") %>% 
  read_csv() %>% 
  knitr::kable(.)

@@

```{r}
#| label: tbl-cv-over-time
#| tbl-cap: "Summary of significance tests for CV values between the two chronological phases"

@@

# apply mslr test to each variable (row with a tibble)
# Krishnamoorthy and Lee’s (2014) modified signed-likelihood ratio test
# this is a table we can show in the text
table_mslr_test_results_for_phase_differences <-
  df_sitename_nested %>%
  mutate(mslr_result = map_df(data, ~mslr_test(nr = 1e4,
                                               .$value,
                                               .$SPstage.Stage))) %>%
  unnest(mslr_result) %>%
  dplyr::select(-data) %>% 
  # round numeric columns to 3 decimal places
  mutate(across(where(is.numeric), round, 3)) %>% 
  arrange(desc(p_value))

@@

knitr::kable(table_mslr_test_results_for_phase_differences,
             digits = 3)
